A Greedy-based calculation method of RBS maximum allowable current

### 2023-05-22 paper/main.tex
add some cites, fix arrows in figures

Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs. \ref{fig:sp1} to \ref{fig:sp4}.  % TODO: fig 4 个cell的SP（fig:sp1,2,3,4），最终求解结果 fig:ef-mac
According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
In the first iteration, the $SP$s of all four batteries are selected, and the switch states on the paths are set to ON. 
The corresponding $\bm{X}_s$ are calculated using the previous method, and the currents of the batteries are obtained as $u_b/r_b$, $u_b/r_b$, $u_b/r_b$, and $u_b/r_b$. 
Since all batteries are short-circuited and the current of the battery exceeds the maximum allowed current $I_m$, this solution does not satisfy constraint \ref{eq:Ib_leq_Im} and is discarded. 
The second iteration is carried out using the dichotomy method, and two batteries are selected for the combination. 
Assuming that the selected combinations are $(B1, B2)$, the $\bm{X}_s$ obtained according to the $SP$s are substituted into the previous calculation, and the current of each battery is $u_b/r_b$, $u_b/r_b$, $0$, and $0$. 
This solution meets the condition. 
After that, the case of selecting three cells is considered. 
By similar calculations, it is determined that all solutions do not satisfy the constraint when three cells are selected. 
Finally, the MAC of this structure is $\eta=2$, and the related result is shown in Fig. \ref{fig:ef-mac} and Tab. \ref{tab:find_mac}.

@@

The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
According to the results shown in Tab. \ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$. 
This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances. 
This increases the difficulty and uncertainty in RBS structure design. 
On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs. \ref{tab:given_x} and \ref{tab:find_mac}.
$\eta$ only reflects the maximum output current capability of the RBS structure.
Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure. 
Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
Most of the currently proposed RBS structures have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. % #TODO 添加cite
However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated. 
The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.

>>>>

Firstly, the weight $N_s$ in Eq. \ref{eq:weight} represents the total number of switches in the system, which is 19. 
By using this formula and the Dijkstra search strategy, the $SP$s of each cell can be obtained, as shown in Figs. \ref{fig:sp1} to \ref{fig:sp4}.
According to the greedy strategy, as many $SP$s as possible should be selected to get the MAC. 
In the first iteration, the $SP$s of all four batteries are selected, and the switch states on the paths are set to ON. 
The corresponding $\bm{X}_s$ are calculated using the previous method, and the currents of the batteries are obtained as $u_b/r_b$, $u_b/r_b$, $u_b/r_b$, and $u_b/r_b$. 
Since all batteries are short-circuited and the current of the battery exceeds the maximum allowed current $I_m$, this solution does not satisfy constraint \ref{eq:Ib_leq_Im} and is discarded. 
The second iteration is carried out using the dichotomy method, and two batteries are selected for the combination. 
Assuming that the selected combinations are $(B1, B2)$, the $\bm{X}_s$ obtained according to the $SP$s are substituted into the previous calculation, and the current of each battery is $u_b/r_b$, $u_b/r_b$, $0$, and $0$. 
This solution meets the condition. 
After that, the case of selecting three cells is considered. 
By similar calculations, it is determined that all solutions do not satisfy the constraint when three cells are selected. 
Finally, the MAC of this structure is $\eta=2$, and the related result is shown in Fig. \ref{fig:ef-mac} and Tab. \ref{tab:find_mac}.

@@

The correctness of the results shown in Fig. \ref{fig:ef-mac} is obvious. 
When B1 and B2 or B3 and B4 are connected in parallel, the RBS can output the maximum current, which is $\eta=2$, i.e. twice the current output of a single battery in RBS.
While adding more batteries to the main circuit can only form a series structure and will not improve the MAC.
It is worth noting that when solving for MAC, $\eta$ is used as the objective function instead of $I_o$, which makes the result of MAC more reasonable. 
According to the results shown in Tab. \ref{tab:find_mac}, $I_o$ and $\bm{I}_b$ are affected by the equivalent resistance $R_o$ of external electrical appliance, the battery's electromotive force $u_b$, and internal resistance $r_b$. 
This means that if $I_o$ is used as the objective function, even for the same RBS structure, the MAC result and corresponding switch state could be changed due to different external electrical appliances. 
This increases the difficulty and uncertainty in RBS structure design. 
On the contrary, by using $\eta$ as the objective function, which dividing $I_o$ and $\max\bm{I}_b$, the influence of these factors on the results is eliminated, as shown in Tabs. \ref{tab:given_x} and \ref{tab:find_mac}.
$\eta$ only reflects the maximum output current capability of the RBS structure.
Assuming that the maximum allowed current of battery cells in the RBS is $I_m$, the maximum output current of the RBS structure can be calculated as $\eta I_m$ by calculating the $\eta$ of the structure. 
Therefore, compared to $I_o$, $\eta$ is more suitable for structure design. 
Most of the currently proposed RBS structures\cite{ciNovelDesignAdaptive2007,alahmadBatterySwitchArray2008,kimDependableEfficientScalable2010b,kimBalancedReconfigurationStorage2011a,taesickimSeriesconnectedSelfreconfigurableMulticell2012a,6843711} have simple topological characteristics, and the calculation of MACs are relatively simple, even intuitive. % #TODO 添加cite
However, when complex and flexible structures need to be designed for application scenarios such as equalization or isolation of specific battery cells, the estimation of MAC will become complex and complicated. 
The method proposed in this paper can effectively solve any RBS structure and estimate MAC universally, paving the way for the structure design of more complex and flexible RBSs.
